External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

\section{The Denoising Algorithm}
\subsection{Fast Internal Patch Group Searching}

@@

To remove the real noise, we employ the sparse coding framework. And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.

@@

\subsection{Discussion on Parameter $\lambda$}
The proposed method only has a key parameter, namely the regularization paramters $\lambda$. To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$. The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$. This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
\begin{figure}
\includegraphics[width=1\linewidth]{images/param.png}
\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
\label{fig10}
\end{figure}

>>>>

\section{The Denoising Algorithm}

In this work, we solve the real noisy image denoising problem by employing the sparse coding framework \cite{pgpd} in Equ. (\ref{equ6}). We utilize two strategies to gain better performance: one is the 'Summed Area Table' \cite{sat} for faster patch group (PG) searching and the other is that the prior weights in Equ. (\ref{equ3}) are used for better denoising effects.

\subsection{Fast Internal Patch Group Searching}

@@

@@

%\subsection{Discussion on Parameter $\lambda$}
%The proposed method only has a key parameter, namely the regularization paramters $\lambda$. To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$. The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$. This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
%\begin{figure}
%\includegraphics[width=1\linewidth]{images/param.png}
%\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
%\label{fig10}
%\end{figure}
